Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-11 summary.tex
new refs removed last sentence

Beam helicity and beam charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.  This new data set is larger than the previously publised 1996-2005 data set Ref.~\cite{2009a}.

A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 DVCS/BH event sample. The \blue{resulting} asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this simultaneous extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic of the beam charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data. \blue{These model fits all include the H{\sc ermes} data set from 1996-2005. One fitted model achieve good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. One leading-twist model shows good agreement with the asymmetry amplitudes that it can be used to calculate. }

>>>>

Beam helicity and beam charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.  This new data set is larger than the previously publised 1996-2005 data set Ref.~\cite{Air09}.

A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 DVCS/BH event sample. The \blue{resulting} asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this simultaneous extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic of the beam charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data. \blue{These model fits all include the H{\sc ermes} data set from 1996-2005. One fitted model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.}
